%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/cheuk-lau-31311626/}{\Large Cheuk Lau}} & Email : \href{mailto:cheuk.lau@aggienetwork.com}{cheuk.lau@aggienetwork.com}\\
  \href{https://www.linkedin.com/in/cheuk-lau-31311626/}{https://www.linkedin.com/in/cheuk-lau-31311626/} & Mobile : +1-518-915-8165 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Insight}{Palo Alto, CA}
      {DevOps Engineering Fellows Program}{Jul. 2018 -- Present}
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {Doctorate of Philosophy in Computational Physics;  GPA: 3.80}{Aug. 2011 -- May. 2016}
    \resumeSubheading
      {Pennsylvania State University}{University Park, PA}
      {Master of Science in Nuclear Engineering;  GPA: 3.90}{Jan. 2009 -- Dec. 2010}
    \resumeSubheading
      {University of Illinois}{Urbana-Champaign, IL}
      {Bachelor of Science in Nuclear Engineering;  GPA: 3.50}{Aug. 2004 -- May. 2008}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Insight}{Palo Alto, CA}
      {DevOps Fellow}{Jul. 2018 - Present}
      \resumeItemListStart
        \resumeItem{Project Name}
          {Provide the project description here, making this long because I suspect this should take a minimum of two lines (list software used here).}
      \resumeItemListEnd

    \resumeSubheading
      {Lawrence Livermore National Laboratory}{Livermore, CA}
      {Computational Physicist}{Jul. 2016 - Jul. 2018}
      \resumeItemListStart
        \resumeItem{Code Verification}
          {Developed automated testing of scientific codes using standard verification and validation procedures (C++, Python, Bash).}
        \resumeItem{Code Developer}
          {Implemented and tested new methods from academic journals to further the capability of scientific codes in multiple disciplines e.g., plasma physics, fluid dynamics, radiation transport (C++, Git).}
        \resumeItem{Mentor}
          {Provided guidance and technical direction to PhD-level summer interns.}
        \resumeItem{Publications}
          {\href{https://doi.org/10.3847/1538-4365/aa7ff5}{https://doi.org/10.3847/1538-4365/aa7ff5}, \href{https://e-reports-ext.llnl.gov/pdf/888520.pdf}{https://e-reports-ext.llnl.gov/pdf/888520.pdf}}
      \resumeItemListEnd

    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {National Excellence Fellow}{Aug. 2011 - May. 2016}
      \resumeItemListStart
        \resumeItem{Code Developer}
          {Research on adaptive mesh refinement strategies for optimizing the computational efficiency of radiation transport codes (C++, Matlab, Git).}
        \resumeItem{Publications}
          {\href{https://doi.org/10.13182/NSE16-28}{https://doi.org/10.13182/NSE16-28}, \href{http://oaktrust.library.tamu.edu/handle/1969.1/158050}{http://oaktrust.library.tamu.edu/handle/1969.1/158050}}
      \resumeItemListEnd

    \resumeSubheading
      {Knolls Atomic Power Laboratory}{Niskayuna, NY}
      {Nuclear Engineer}{Aug. 2008 - Aug. 2011}
      \resumeItemListStart
        \resumeItem{Code Developer}
          {Implemented and tested new methods from academic journals to further the capability of radiation transport codes (C++, Fortran, Git).}
        \resumeItem{Field Testing}
          {Gathered instrumentation data from aircraft carriers and submarines for code validation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{TradeUp}
      {App allowing users to manage their trading card game (TCG) inventory, view other users' inventory in the same location, and propose in-person trades. Item values update in real-time using third-party APIs.}
    \resumeSubItem{Catalog App}
      {\href{https://github.com/cheuklau/catalog_app}{\bf https://github.com/cheuklau/catalog\_app} Sample app built on Flask demonstrating create, read, update and delete (CRUD) functionalities using an SQL backend with third-party authentication.}
    \resumeSubItem{Neighborhood App}
      {\href{https://github.com/cheuklau/neighborhood_app}{\bf https://github.com/cheuklau/neighborhood\_app} Sample app demonstrating the use of Javascript libraries (Knockout JS) and multiple third-party APIs (Google Maps and New York Times).}
    \resumeSubItem{Adaptive Angular Quadrature}
      {\href{https://github.com/cheuklau/phd_research}{\bf https://github.com/cheuklau/phd\_research} PhD work developing linear discontinuous finite-element based angular quadratures.}
  \resumeSubHeadingListEnd

%
%--------CERTIFICATIONS------------
\section{Certifications -- available upon request}
  \resumeSubHeadingListStart
    \resumeSubItem{Udemy DevOps}
      {Series of courses on DevOp tools (Docker, Kubernetes, Jenkins, Terraform, Prometheus).}
    \resumeSubItem{Udacity Full-Stack Engineering Nano-Degree}
      {Certificate covering both front and backend development along with server deployment. (HTML, CSS, Javascript, jQuery, Knockout JS, Flask, SQL, Apache, AWS).}
    \resumeSubItem{DataCamp Data Scientist with Python}
      {Certificate covering data manipulation, visualization, statistics and machine learning (Pandas, NumPy, Scikit-Learn).}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
